### 2020-09-07 cv/cv-body.tex
Fix f1000
Fix typo
Add Litzow et al. 2020
Add pubs

\begin{description}
\tightlist
\item[2020]
\textbf{Anderson, S.C.}, Mulberry, N., Edwards, A.M., Stockdale, J.E.,
Iyaniwura, S.A., Falcao, R.C., Otterstatter, M.C., Janjua, N.Z., Coombs,
D., and Colijn, C. 2020. How much leeway is there to relax COVID-19
control measures? medRxiv 2020.06.12.20129833.
\url{https://doi.org/10.1101/2020.06.12.20129833}.
\item[2020]
\textbf{Anderson, S.C.}, A.M. Edwards, M. Yerlanov, N. Mulberry, J.
Stockdale, S.A. Iyaniwura, R.C. Falcao, M.C. Otterstatter, M.A.\ Irvine,
N.Z. Janjua, D. Coombs, C. Colijn. Estimating the impact of COVID-19
control measures using a Bayesian model of physical distancing. medRxiv
2020.04.17.20070086. \url{https://doi.org/10.1101/2020.04.17.20070086}.
\end{description}

@@

@@

transparency, assessment efficiency, and monitoringy. In press at

@@

@@

>>>>

\begin{description}
\tightlist
\item[2020]
\textbf{Anderson, S.C.}, Mulberry, N., Edwards, A.M., Stockdale, J.E.,
Iyaniwura, S.A., Falcao, R.C., Otterstatter, M.C., Janjua, N.Z., Coombs,
D., and Colijn, C. 2020. How much leeway is there to relax COVID-19
control measures? medRxiv 2020.06.12.20129833.
\url{https://doi.org/10.1101/2020.06.12.20129833}.
\end{description}

@@

\textbf{Anderson, S.C.}, A.M. Edwards, M. Yerlanov, N. Mulberry, J.
Stockdale, S.A. Iyaniwura, R.C. Falcao, M.C. Otterstatter, M.A.\ Irvine,
N.Z. Janjua, D. Coombs, C. Colijn. Estimating the impact of COVID-19
control measures using a Bayesian model of physical distancing. In press
at PLOS Computational Biology. Preprint: medRxiv 2020.04.17.20070086.
\url{https://doi.org/10.1101/2020.04.17.20070086}.
Cahill, C.L., \textbf{S.C. Anderson}, A.J. Paul, L. MacPherson, M.G.
Sullivan, B.T. van Poorten, C.J. Walters, and J.R. Post. A
spatial-temporal approach to modeling somatic growth across inland
recreational fisheries landscapes. In press at Canadian Journal of
Fisheries and Aquatic Sciences.
\url{https://doi.org/10.1139/cjfas-2019-0434}.
Litzow, M.A., M.E. Hunsicker, E.J. Ward, \textbf{S.C. Anderson}, J. Gao,
S. Zador, S. Batten, S. Dressel, J. Duffy-Anderson, E. Fergusson, R.
Hopcroft, B.J. Laurel, and R. O'Malley. Evaluating ecosystem change as
Gulf of Alaska temperature exceeds the limits of preindustrial
variability. Progress in Oceanography. 186:102393.
\url{https://doi.org/10.1016/j.pocean.2020.102393}.

@@

transparency, assessment efficiency, and monitoring. In press at

@@

\href{https://facultyopinions.com/prime/718498042}{F1000 Prime
recommended}.

@@

\href{https://f1000.com/prime/9542957}{F1000 Prime recommended}.
